Componentes Passivos em RF

### 2024-11-21 Lab09 - IP3-meas_prj/Docs/article/article.qmd
asdkjlfhasdf

a1_diode = Is/VT 
a2_diode = Is/VT**2/2 
a3_diode = Is/VT**3/6
IP3h_diode = 2*math.sqrt(abs(a1_diode)/abs(a3_diode))
IP3i_diode = IP3h_diode/math.sqrt(3)
```

@@

# Intervalo de Vi
Vi = np.logspace(np.log10(700e-6), np.log10(2), 1000)

a1_diode_generic = yD
a3_diode_generic = yD/VT

# Cálculo de Io
Io1 = a1_diode_generic * Vi
Io3 = 3/4 * a3_diode_generic * Vi**3

@@

# Plot log-log
plt.figure(figsize=(8, 6))
plt.loglog(Vi, Io1, linestyle="-", color="blue", label=r"$I_{o1}$")
plt.loglog(Vi, Io3, linestyle="-", color="green", label=r"$I_{o3}$")
plt.axhline(I_IP3, color="red", linestyle=":", label=f"$OIP3 = {I_IP3:.2e}$ A")
plt.axvline(Vi_IP3, color="purple", linestyle=":", label=f"$IIP3 = {Vi_IP3:.2e}$ V")
plt.xlabel(r"$V_i$ (V)", fontsize=12)
plt.ylabel(r"$I_o$ (A)", fontsize=12)
plt.title("Gráfico log-log de $I_{o1}$ e $I_{o3}$ vs $V_i$", fontsize=14)
plt.grid(which="both", linestyle="--", linewidth=0.5)
plt.legend(fontsize=10)
plt.tight_layout()
plt.show()

Io3
```

>>>>

a1_diode_0 = Is/VT 
a2_diode_0 = Is/VT**2/2 
a3_diode_0 = Is/VT**3/6
IP3h_diode = 2*math.sqrt(abs(a1_diode_0)/abs(a3_diode_0))
IP3i_diode = IP3h_diode/math.sqrt(3)
```

@@

# Intervalo de Vi
Vi = np.logspace(np.log10(700e-6), np.log10(2), 10000)

a1_diode = yD
a3_diode = yD/(6*VT**2)

# Cálculo de Io
Io1 = a1_diode * Vi
Io3 = 3/4 * a3_diode * Vi**3

@@

# Plot log-log
plt.figure(figsize=(8, 6))
plt.loglog(Vi, Io1, linestyle="-", color="blue", label=r"$I_{o1}$")
plt.loglog(Vi, Io3, linestyle="-", color="green", label=r"$I_{o3}$")
plt.axhline(I_IP3, color="red", linestyle=":", label=f"$OIP3 = {I_IP3:.5e}$ A")
plt.axvline(Vi_IP3, color="purple", linestyle=":", label=f"$IIP3 = {Vi_IP3:.5e}$ V")
plt.xlabel(r"$V_i$", fontsize=12)
plt.ylabel(r"$I_o$", fontsize=12)
plt.title(r"Gráfico $IP_{3i}$", fontsize=14)
plt.grid(which="both", linestyle="--", linewidth=0.5)
plt.legend(fontsize=10)
plt.tight_layout()
plt.show()
```
